Imputation/denoising

### 2020-05-04 main_figures/imputation.Rmd
updated imputation figure with new color mapping

e <- do.call(cbind, ll2)
o <- names(sort(rowMeans(e, na.rm=TRUE)+rowMedians(e, na.rm=TRUE), decreasing=TRUE))
ll2 <- lapply(ll2, FUN=function(x) x[o,])
ll2s <- lapply(ll2, scale)

>>>>

e <- do.call(cbind, ll2)
o <- names(sort(rowMeans(e, na.rm=TRUE)+rowMedians(e, na.rm=TRUE), decreasing=TRUE))
ll2 <- lapply(ll2, FUN=function(x) x[o,])
ll2s <- lapply(ll2, pipeComp::colCenterScale)
